Miniproject - Algebraic Geometry

### 2021-12-07 Algebraic geometry/submission.tex
Fixed minor issues in alg geo
Added part III (vi) to ant and fixed some minor points in all miniprojects
Finished sketch of the lemma on the leading term ideal of I(Gr(2, V))

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{listings}
\usepackage[style=english]{csquotes}
\usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}

@@

\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Proj}{\mathbb{P}}
\newcommand{\Aff}{\mathbb{A}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\extpow}{\mathchoice{{\textstyle\bigwedge}}
    {{\bigwedge}}
    {{\textstyle\wedge}}
    {{\scriptstyle\wedge}}}
\newcommand{\vspan}{\mathrm{span}}
\newcommand{\divides}{\ | \ }
\newcommand\restr[2]{{
    \left.\kern-\nulldelimiterspace
    #1
    \vphantom{\big|}
    \right|_{#2}
}}

@@

\begin{lemma}
    \label{prop:basic_properties_exterior_product}
    Let $v_1, ..., v_d \in V$. Have for $\pi \in S_d$ that
    \begin{equation*}
        v_{\pi(1)} \wedge ... \wedge v_{\pi(k)} = \sgn(\pi) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
    Furthermore if $v_i = v_j$ for some $i \neq j$, then
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
\end{lemma}
\begin{proof}
    Note that
    \begin{equation*}
        u \otimes v \otimes v' \otimes w = -(u \otimes v' \otimes v \otimes w)
    \end{equation*}
    for all $u \in \extpow^{i - 1}(V), w \in \extpow^{(d - i - 1)}(V), v, v' \in V$.

@@

    Furthermore, we find that
    \begin{equation*}
        u \otimes v \otimes v \otimes w = -(u \otimes v \otimes v \otimes w) = 0
    \end{equation*}
    must be zero.
    Hence, if $v_1, ..., v_d \in V$ with $v_i = v_j$ for some $i \neq j$, then there is a permutation $\pi \in S_d$ with $\pi(1) = i, \pi(2) = j$ and
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = (\sgn(\pi))(v_i \wedge v_j \wedge v_{\pi(3)} \wedge ... \wedge v_{\pi(k)}) = \sgn(\pi) 0 = 0
    \end{equation*}
\end{proof}

@@

\begin{lemma}
    \label{prop:linear_transform_extpow}
    Let $A = (a_{ij}) \in \GL_d(k)$ and $v_1, ..., v_d \in V$.
    Then
    \begin{equation*}
        \Bigl( \sum_j a_{1j}v_j \Bigl) \wedge ... \wedge \Bigl( \sum_{j} a_{dj} v_j \Bigr) = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
\end{lemma}
\begin{proof}
    By a direct computation using Lemma~\ref{prop:basic_properties_exterior_product}, we find
    \begin{align*}
        &\Bigl( \sum_j a_{ij} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \sum_{j_1, ..., j_d} a_{1j_1} ... a_{dj_d} (v_{j_1} \wedge ... \wedge v_{j_d}) \\
        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} (v_{\pi(1)} \wedge ... \wedge v_{\pi(d)}) \\
        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} \sgn(\pi) (v_1 \wedge ... \wedge v_d) \\
        = &(v_1 \wedge ... \wedge v_d) \ \sum_{\pi \in S_d} \sgn(\pi) \prod_{j = 1}^d a_{j\pi(j)} = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{align*}
    where the last equality holds due to the Leibniz determinant formula.
\end{proof}
\begin{lemma}
    \label{prop:extpow_zero_iff_independent}
    For $v_1, ..., v_d \in V$ have
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = 0 \ \Leftrightarrow \ v_1, ..., v_d \ \text{linearly dependent}
    \end{equation*}
\end{lemma}
\begin{proof}
    For the direction $\Rightarrow$, assume that $v_1, ..., v_d$ are not independent. 
    Then there is a nonzero vector $a_1 \in k^d$ with $\sum a_{1i} v_i = 0$.
    Clearly, we can extend $a_1$ to a basis $a_1, ..., a_d$ of $k^d$, which gives a matrix $A = (a_{ij}) \in \GL_d(k)$.

@@

    Direction $\Leftarrow$ TODO
\end{proof}
\begin{lemma}
    \label{prop:subspace_closed}
    Let $v \in V$ and $u \in \extpow^{d - 1} U$ for a linear subspace $U \leq V$. 
    If $v \wedge u \in \extpow^d U$ then $v \in U$ or $u = 0$.
\end{lemma}
\begin{proof}
    TODO
\end{proof}

@@

    It follows that $\dim(\extpow^d k^n) = \dim(\Proj^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
\end{proof}
\begin{corollary}[2b]
    \label{prop:image_phi}
    Let $\bar{f}: \Proj(\extpow^d k^n) \to \Proj^{{n \choose d} - 1}$ be the map $f$ from before modulo $k^*$.
    Then
    \begin{equation*}
        \rho = f \circ \phi
    \end{equation*}
    and in particular, we see that $\phi(Gr(d, n))$ is a projective variety and isomorphic to $\rho(\Gr(d, n))$.
\end{corollary}
\begin{proposition}[2c]
    The map $\phi$ is injective.
\end{proposition}
\begin{proof}
    Consider two $d$-dimensional subspaces $U, W$ of $k^n$ with $\phi(U) = \phi(W)$.
    Let $u_1, ..., u_l$ be a basis of $U \cap W$ and extend it to bases $u_1, ..., u_d$ of $U$ and $u_1, ..., u_l, w_{l + 1}, ..., w_d$ of $W$.
    As $\phi(U) = \phi(W)$, we can assume that the $u_i, w_i$ are scaled such that
    \begin{align*}
        0 =& (u_1 \wedge ... \wedge u_d) - (u_1 \wedge ... \wedge u_l \wedge w_{l + 1} \wedge ... \wedge w_d) \\
        =& u_1 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr)
    \end{align*}
    By Lemma~\ref{prop:subspace_closed} we see that
    \begin{equation*}
        u_2 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr) = 0
    \end{equation*}
    as $u_1 \notin \vspan\{u_2, ..., u_d, w_{l + 1}, ..., w_d\}$.
    Inductively, this argument shows that
    \begin{equation*}
        (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
    \end{equation*}
    If $l < d$, we can now apply Lemma~\ref{prop:subspace_closed} again to see that
    \begin{equation*}
        u_{l + 1} \in \vspan\{ u_{l + 2}, ..., u_d, w_{l + 1}, ..., w_d \}
    \end{equation*}
    as $u_{l + 2} \wedge ... \wedge u_d \neq 0$ by Lemma~\ref{prop:extpow_zero_iff_independent}.
    However, this contradicts the linear independence of $u_{l + 1}, ..., u_d, w_{l + 1}, ..., w_d$.
    Hence it must be $l = d$ and so $U = W$.
\end{proof}

@@

    \lstinputlisting{./examples.sage}

@@

\end{document}

>>>>

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage[style=english]{csquotes}
\usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}

@@

\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Proj}{\mathbb{P}}
\newcommand{\Aff}{\mathbb{A}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\contradiction}{\lightning}
\newcommand{\extpow}{\mathchoice{{\textstyle\bigwedge}}
    {{\bigwedge}}
    {{\textstyle\wedge}}
    {{\scriptstyle\wedge}}}
\newcommand{\vspan}{\mathrm{span}}
\newcommand{\divides}{\ | \ }
\newcommand\restr[2]{{
    \left.\kern-\nulldelimiterspace
    #1
    \vphantom{\big|}
    \right|_{#2}
}}

@@

\begin{lemma}
    \label{prop:basic_properties_exterior_product}
    Let $v_1, ..., v_d \in V$. Have for $\pi \in S_d$ that
    \begin{equation*}
        v_{\pi(1)} \wedge ... \wedge v_{\pi(k)} = \sgn(\pi) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
    Furthermore if $v_i = v_j$ for some $i \neq j$, then
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
\end{lemma}
\begin{proof}
    Note that
    \begin{equation*}
        u \wedge v \wedge v' \wedge w = -(u \wedge v' \wedge v \wedge w)
    \end{equation*}
    for all $u \in \extpow^{i - 1}(V), w \in \extpow^{(d - i - 1)}(V), v, v' \in V$.

@@

    Furthermore, we find that
    \begin{equation*}
        u \wedge v \wedge v \wedge w = -(u \wedge v \wedge v \wedge w) = 0
    \end{equation*}
    must be zero.
    Hence, if $v_1, ..., v_d \in V$ with $v_i = v_j$ for some $i \neq j$, then there is a permutation $\pi \in S_d$ with $\pi(1) = i, \pi(2) = j$ and
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = (\sgn(\pi))(v_i \wedge v_j \wedge v_{\pi(3)} \wedge ... \wedge v_{\pi(k)}) = \sgn(\pi) 0 = 0
    \end{equation*}
\end{proof}

@@

\begin{lemma}
    \label{prop:linear_transform_extpow}
    Let $A = (a_{ij}) \in \GL_d(k)$ and $v_1, ..., v_d \in V$.
    Then
    \begin{equation*}
        \Bigl( \sum_j a_{1j}v_j \Bigl) \wedge ... \wedge \Bigl( \sum_{j} a_{dj} v_j \Bigr) = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
\end{lemma}
\begin{proof}
    By a direct computation using Lemma~\ref{prop:basic_properties_exterior_product}, we find
    \begin{align*}
        &\Bigl( \sum_j a_{ij} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \sum_{j_1, ..., j_d} a_{1j_1} ... a_{dj_d} (v_{j_1} \wedge ... \wedge v_{j_d}) \\
        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} (v_{\pi(1)} \wedge ... \wedge v_{\pi(d)}) \\
        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} \sgn(\pi) (v_1 \wedge ... \wedge v_d) \\
        = &(v_1 \wedge ... \wedge v_d) \ \sum_{\pi \in S_d} \sgn(\pi) \prod_{j = 1}^d a_{j\pi(j)} = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{align*}
    where the last equality holds due to the Leibniz determinant formula.
\end{proof}
\begin{lemma}
    \label{prop:extpow_zero_iff_independent}
    For $v_1, ..., v_d \in V$ have
    \begin{equation*}
        v_1 \wedge ... \wedge v_d = 0 \ \Leftrightarrow \ v_1, ..., v_d \ \text{linearly dependent}
    \end{equation*}
\end{lemma}
\begin{proof}
    For the direction $\Leftarrow$, assume that $v_1, ..., v_d$ are not independent. 
    Then there is a nonzero vector $a_1 \in k^d$ with $\sum a_{1i} v_i = 0$.
    Clearly, we can extend $a_1$ to a basis $a_1, ..., a_d$ of $k^d$, which gives a matrix $A = (a_{ij}) \in \GL_d(k)$.

@@

    Direction $\Rightarrow$ TODO
\end{proof}
\begin{lemma}
    \label{prop:subspace_closed}
    Let $v \in V$ and $u \in \extpow^{d - 1} U$ for a linear subspace $U \leq V$. 
    If $v \wedge u \in \extpow^d U$ then $v \in U$ or $u = 0$.
\end{lemma}
\begin{proof}
    TODO
\end{proof}

@@

    It follows that $\dim(\extpow^d k^n) = \dim(\Proj^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
\end{proof}
\begin{corollary}[2b]
    \label{prop:image_phi}
    Let $\bar{f}: \Proj(\extpow^d k^n) \to \Proj^{{n \choose d} - 1}$ be the map $f$ from before modulo $k^*$.
    Then
    \begin{equation*}
        \rho = \bar{f} \circ \phi
    \end{equation*}
    and in particular, we see that $\phi(Gr(d, n))$ is a projective variety and isomorphic to $\rho(\Gr(d, n))$.
\end{corollary}
\begin{proposition}[2c]
    The map $\phi$ is injective.
\end{proposition}
\begin{proof}
    Consider two $d$-dimensional subspaces $U, W$ of $k^n$ with $\phi(U) = \phi(W)$.
    Let $u_1, ..., u_l$ be a basis of $U \cap W$ and extend it to bases $u_1, ..., u_d$ of $U$ and $u_1, ..., u_l, w_{l + 1}, ..., w_d$ of $W$.
    As $\phi(U) = \phi(W)$, we can assume that the $u_i, w_i$ are scaled such that
    \begin{align*}
        0 =& (u_1 \wedge ... \wedge u_d) - (u_1 \wedge ... \wedge u_l \wedge w_{l + 1} \wedge ... \wedge w_d) \\
        =& u_1 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr)
    \end{align*}
    By Lemma~\ref{prop:subspace_closed} we see that
    \begin{equation*}
        u_2 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr) = 0
    \end{equation*}
    as $u_1 \notin \vspan\{u_2, ..., u_d, w_{l + 1}, ..., w_d\}$.
    Inductively, this argument shows that
    \begin{equation*}
        (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
    \end{equation*}
    If $l < d$, we can now apply Lemma~\ref{prop:subspace_closed} again to see that
    \begin{equation*}
        u_{l + 1} \in \vspan\{ u_{l + 2}, ..., u_d, w_{l + 1}, ..., w_d \}
    \end{equation*}
    as $u_{l + 2} \wedge ... \wedge u_d \neq 0$ by Lemma~\ref{prop:extpow_zero_iff_independent}.
    However, this contradicts the linear independence of $u_{l + 1}, ..., u_d, w_{l + 1}, ..., w_d$.
    Hence it must be $l = d$ and so $U = W$.
\end{proof}

@@

    \lstinputlisting[language = python]{./examples.sage}
    This shows that the degree of $\Gr(2, 5)$ is indeed 5, as expected.

@@

To investigate the properties of $\phi(\Gr(2, n))$ for larger $n$, we use one tool I encountered during an earlier course on Computational Commutative Algebra and Algebraic Geometry.
\begin{proposition}[Macaulay Basis Theorem]
    Let $\preceq$ be a graded monomial ordering on $R = k[x_0, ..., x_n]$.
    Then for an ideal $I \leq R$ have that the monomials $x_0^{\alpha_0} ... x_n^{\alpha_n} \notin \mathrm{lt}(I)$ are a $k$-vector space basis of $R/I$.

    Here $\mathrm{lt}(I)$ is the leading term ideal of $I$, i.e. the ideal generated by the leading terms of all $f \in I$, w.r.t. $\preceq$.
\end{proposition}
\begin{proof}
    See \cite{kreuzer}.
\end{proof}
\begin{lemma}
    Define the graded reverse monomial ordering $\preceq$ on $R := k[x_{i, j} \ | \ i < j]$ where the variables $x_{i, j}$ are ordered co-lexicographically w.r.t. $(i, j)$, i.e.
    \begin{equation*}
        x_{i, j} \leq x_{u, v} \ :\Leftrightarrow \ (i, j) \leq_{\text{colex}} (u, v)
    \end{equation*}
    Moreover, let
    \begin{equation*}
        I := \langle x_{i, j}x_{u, v} + x_{i, v}x_{j, u} - x_{i, u}x_{j, v} \ | \ i < j < u < v \rangle \leq R
    \end{equation*}
    be the ideal defining $\phi(\Gr(d, V))$ that was considered above. Then
    \begin{equation*}
        \mathrm{lt}(I) = J := \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle \leq R
    \end{equation*}
\end{lemma}
\begin{proof}
    Note that for $i < j < u < v$ have $x_{u, v}, x_{j, v} \succ x_{i, v} \succ x_{i, j}, x_{i, u}, x_{j, u}$.
    Thus the leading term of $x_{i, j} x_{u, v} + x_{i, v} x_{j, u} - x_{i, u} x_{j, v}$ is
    \begin{equation*}
        \mathrm{lt}(x_{i, j} x_{u, v} + x_{i, v} x_{j, u} - x_{i, u} x_{j, v}) = x_{i, v} x_{j, u}
    \end{equation*}
    It follows that $J \subseteq \mathrm{lt}(I)$.

    For the other direction, we use a quite lengthy degree argument.
    Sadly, the argument I found is quite full of technical detail.
    I try to present it as clearly as possible, at the cost of being not always completely formal. 
    But honestly, the proof contains enough indices already.

    Consider homogeneous polynomials $f_{i, j, u, v} \in R$ and
    \begin{equation*}
        F = \sum_{i < j < u < v} f_{i, j, u, v} \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})
    \end{equation*}
    We want to show that $\mathrm{lt}(F) \in J$.

    Let
    \begin{equation*}
        f_{i, j, u, v} = \sum_{\alpha \in \N^N} c^{(i, j, u, v)}_\alpha x^\alpha
    \end{equation*}
    Then
    \begin{equation*}
        F = \sum_{\alpha \in \N^N} \sum_{i < j < u < v} c^{(i, j, u, v)}_\alpha x^\alpha \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})
    \end{equation*}
    and so there exists $\alpha \in \N^N$ and $\epsilon \in k^*$ with
    \begin{equation*}
        \mathrm{lt}(F) = \epsilon \cdot \mathrm{lt}\Bigl( \sum_{i < j < u < v} c_\alpha^{(i, j, u, v)} x^\alpha \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v}) \Bigr)
    \end{equation*}
    Hence, we may assume wlog that all the $f_{i, j, u, v}$ are scaled monomials.

    Now, observe that all monomials in $F$ are of the form
    \begin{align*}
        \epsilon \ x_{i, v} \ x_{j, u} \ f_{i, j, u, v} \quad \text{or} \quad 
        \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v} \quad \text{or} \quad 
        \epsilon \ x_{i, j} \ x_{u, v} \ f_{i, j, u, v} 
    \end{align*}
    where $\epsilon \in k^*$ and $i < j < u < v$.
    In particular, this is true for the leading term $\mathrm{lt}(F)$.
    In the first of those case, clearly $\mathrm{lt}(F) \in J$.

    So consider now the second case, i.e. $\mathrm{lt}(F) = \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$.
    Since $x_{i, v} \ x_{j, u} \ f_{i, j, u, v} \succ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$, we see that the term $x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ cannot occur in $F$, i.e. must ``cancel out''.
    Hence the monomial $\epsilon \ x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ has a nonzero coefficient in
    \begin{equation*}
        F - f_{i, j, u, v} x_{i, v} x_{j, u} = \sum_{\substack{a < b < c < d\\(a, b, c, d) \neq (i, j, u, v)}} f_{a, b, c, d} \ (x_{a, d} x_{b, c} - x_{a, c} x_{b, d} + x_{a, b} x_{c, d})
    \end{equation*}
    and so for $(a, b, c, d) \neq (i, j, u, v), \epsilon' \in k^*$ have that
    \begin{align*}
        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \quad \text{or}\\
        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, c} \ x_{b, d} \quad \text{or}\\
        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, b} \ x_{c, d}
    \end{align*}
    However, the second and third case imply that $f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$.
    Hence, the ``new'' monomial $f_{a, b, c, d} \ x_{a, d} \ x_{b, c}$ also has to ``cancel out'' in the sum representation of $F$, as comes after $\mathrm{lt}(F) = \epsilon x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$ in the order $\preceq$.
    So applying the whole argument inductively (induction on the number of monomials $\succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$ that occur in any of the polynomials we work with), we end up in the first case
    \footnote{There is a small argument missing here, namely that we apply the next argument on each step of the induction, to show the claim for $f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$. However, it should be easy to see that this is possible.}.

    If $(a, d) = (i, v)$ then $(b, c) \neq (j, u)$ and $x_{b, c} \divides f_{i, j, u, v}$.
    Thus
    \begin{equation*}
        x_{b, c} \ x_{i, u} \ x_{j, v} \divides \mathrm{lt}(F) = \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}
    \end{equation*}
    with $i < j < u < v$ and $i < b < c < v$. 
    No matter how $j, u, b, c$ are ordered relatively to each other, we see that in each possible case $x_{b, c} \ x_{i, u} \ x_{j, v} \in J$:
    \begin{align*}
        j < u < b < c \ &\Rightarrow \ x_{j, v} x_{b, c} \in J \\
        j < b < u < c \ &\Rightarrow \ x_{j, v} x_{b, c} \in J \\
        j < b < c < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
        b < j < u < c \ &\Rightarrow \ f_{i, b, c, v} \ x_{i, c} \ x_{b, v} \succ f_{i, j, u, v} \ x_{i, u} \ x_{j, v} \ \contradiction \\
        b < j < c < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
        b < c < j < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
    \end{align*}
    Hence $\mathrm{lt}(F) \in J$.

    It is now left to consider the case $(b, c) = (j, u)$ and the case $(a, d) \neq (i, v), (b, c) \neq (j, u)$.
    The former can be dealt with in exactly the same way, by noting that $x_{a, d} \divides f_{i, j, u, v}$.
    In the latter case, we even find $x_{a, d} \ x_{b, c} \divides f_{i, j, u, v}$ and a very similar argument works.

    Finally, one must also consider the third ``big'' case, namely that
    \begin{equation*}
        \mathrm{lt}(F) = \epsilon \ x_{i, j} \ x_{u, v} \ f_{i, j, u, v} 
    \end{equation*}
    Again, you can do this similarly as before, but now two monomials ``cancel out''.
    I will not present this here either.
\end{proof}

\printbibliography
\end{document}
